Universal Anonymous Signatures

### 2022-10-01 prism-backend/research/gsac/app-related-proofs.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

\begin{theorem}[Traceability of \CUASGS]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, then \CUASGS is a traceable group signature
  scheme.
\end{theorem}

\begin{proof}
  Assume an adversary \adv~against traceability in \CUASGS. We build an
  adversary \advB against unforgeability of the $(\fissue^1,\feval^0,
  \finsp^{\upk})-\CUASGen$ restriction.

  \advB's simulation of \adv's environment is as in the proof for anonymity
  of \CUASGS. \advB simply outputs whatever \adv~outputs in line 2 of its
  traceability game. Note that, whenever \CUASGS accepts a signature, so does
  \CUASGen. Concretely,
  assume that \adv~wins the traceability game in \figref{fig:model-gs} with
  $\upk \notin \HU \cup \CU$ at line 5. This implies that, in line 14 of the
  \UAS unforgeability game (\figref{fig:exp-uas-unfor}) $\OWNR[\lbrace \cid_i
  \rbrace_{i\in[n]}]$ returns an \uid which is not in either \HU or \CU.
  Similarly, if \adv~wins the traceability game with condition $\Judge(\dots)=0$
  at line 5, then \advB wins its unforgeability game with the corresponding
  check at line 6 in \figref{fig:exp-uas-unfor}.
  %
  \qed
\end{proof}

@@

\begin{theorem}[Unforgeability of \CUASAC]
  \label{thm:forge-cuasac}
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
\end{theorem}

\begin{proof}
  Given \adv~against unforgeability of \CUASAC as defined in \cite{fhs19}, we
  build an adversary \advB against unforgeability of \CUASGen as defined in
  \defref{def:forge-uas}.

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof
  ($ObtIss$ and $Issue$ for \adv~correspond to \OBTISS and \ISSUE for \advB).
  Assume that \adv~wins its game. Note that, since $b=1$ in line 4 of the
  unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
  also returns $1$ in the unforgeability game of \UAS. In addition, if
  there is no corrupt user with a credential containing $D$, then this leads to
  \advB winning at line 12 in \figref{fig:exp-uas-unfor}, as no credential
  owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
  function output $\yeval^0=D$. Thus, \advB wins with the same probability as
  \adv~does.  
  %
  \qed
\end{proof}

>>>>

\begin{theorem}[Traceability of \CUASGS]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
  scheme.
\end{theorem}

\begin{proof}
  Assume an adversary \adv~against traceability in \CUASGS. We build an
  adversary \advB against signature unforgeability of the $(\fissue^1,\feval^0,
  \finsp^{\upk})-\CUASGen$ restriction.

  \advB's simulation of \adv's environment is as in the proof for anonymity
  of \CUASGS. \advB simply outputs whatever \adv~outputs in line 2 of its
  traceability game. Note that, whenever \CUASGS accepts a signature, so does
  \CUASGen. Concretely,
  assume that \adv~wins the traceability game in \figref{fig:model-gs} with
  $\upk \notin \HU \cup \CU$ at line 5. This implies that, in line 10 of the
  \UAS signature unforgeability game (\figref{fig:exp-uas-unfor}) $\OWNR[\lbrace
  \cid_i\rbrace_{i\in[n]}]$ returns an \uid which is not in either \HU or \CU.
  Similarly, if \adv~wins the traceability game with condition $\Judge(\dots)=0$
  at line 5, then \advB wins its signature unforgeability game with the
  corresponding check at line 11 in \figref{fig:exp-uas-unfor}.
  %
  \qed
\end{proof}

@@

\begin{theorem}[Unforgeability of \CUASAC]
  \label{thm:forge-cuasac}
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
\end{theorem}

\begin{proof}
  Given \adv~against unforgeability of \CUASAC as defined in \cite{fhs19}, we
  build an adversary \advB against signature unforgeability of \CUASGen as
  defined in \defref{def:sign-forge-uas}.

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof
  ($ObtIss$ and $Issue$ for \adv~correspond to \OBTISS and \ISSUE for \advB).
  Assume that \adv~wins its game. Note that, since $b=1$ in line 4 of the
  unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
  also returns $1$ in the signature unforgeability game of \UAS. In addition, if
  there is no corrupt user with a credential containing $D$, then this leads to
  \advB winning at line 12 in \figref{fig:exp-uas-unfor}, as no credential
  owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
  function output $\yeval^0=D$. Thus, \advB wins with the same probability as
  \adv~does.  
  %
  \qed
\end{proof}

### 2022-10-01 prism-backend/research/gsac/app-uas-proofs.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

Next, we define the \SimSetup, \ExtractIssue, \ExtractSign functions. \SimSetup
(formally defined in \figref{fig:helper-funcs}) essentially replaces the
\Setup algorithm of each NIZK with the corresponding \NIZKSimSetup algorithm,
and returns the generated parameters along with the
trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
of the corresponding \NIZK scheme, leveraging the trapdoor produced during
\SimSetup. Note that, due to the zero-knowledge and simulation extractability
properties (respectively) of the underlying NIZKs, the result of \SimSetup
is indistinguishable from that of \Setup, and the extracted values match those
used as witnesses in the proofs.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(1^\secpar)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
        \Esecpar). \\
        \Cparm \gets \CSetup(\Csecpar), \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
        \Sparm \gets \SSetup(\Ssecpar), \Eparm \gets \ESetup(\Esecpar) \\
        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
        \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace), \\
        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
      }

@@

% \subsection{Issuance Unforgeability}

% \begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
%   We show that the probability that \fissue outputs a wrong $\yinsp$ value is
%   negligible, as well as the probability that the credential identifier does not
%   belong to an existing (honest or corrupt) user.

%   Observe that the adversary is required to output a credential identifier for
%   which associated entries in \trans and \CRED exist; moreover, if such a
%   credential was produced by an issuer, we must have access to those entries, as
%   issuers are assumed to be honest in this game.
%   %
%   Since we can access $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains
%   a NIZK proof $\NIZKproof_{\Issue}$ proving knowledge by the user of a witness
%   in $\NIZKRel_{\Issue}$, which is simulation extractable, \ExtractIssue
%   produces a tuple $(\upk,\usk,\lbrace (\cid_i,\attrs_i,\cred_i)
%   \rbrace_{i\in[n]}$.
%   %
%   From the fact that issuers are honest, we know that $\ATTR[\cid]$ must match
%   the attribute set \attrs used by user and issuer in the issuance protocol.
%   Thus, from  soundness of the NIZK system, the $(\upk,\lbrace (\cid_i,\attrs_i,
%   \cred_i) \rbrace_{i\in[n]}$ values within the extracted tuple, along with
%   $\ATTR[\cid] = \attrs$ must make \fissue output \yissue, except with
%   negligible probability. Moreover, soundness of the NIZK system also implies
%   that all credentials are bound to the same \usk, which is associated to the
%   extracted \upk.

%   Finally, suppose that the extracted \upk does not belong to a \uid in
%   $\HU \cup \CU$. Then, the produced credential is a forgery. \todo{How to
%     extract the forgery in this case?? I think that expanding the definition
%     so that it requires \adv~to produce a valid signature would make things
%     much easier...}
%   \qed
% \end{proof}

\subsection{Unforgeability}

\begin{proof}[\thmref{thm:forge-uas}; Signature unforgeability of \CUASGen]
  We show that an adversary \adv~winning \ExpForge can be used to break the
  one-more unforgeability property of \SBCM.

  If the verification at line 4 of \ExpForge holds, then $(\msg,\feval,
  \yeval,\cinsp,\sipk,\opk) \in \NIZKLang^{\Sign}$. Then:
  %

@@

  \paragraph{(b) All used credentials were correctly issued.} %
  Since issuers are assumed to be honest, we have access to the $\trans[\cid_i]$
  transcript for all credentials involved in producing the signature. Given
  simulation extractability of $\NIZK^{\Issue}$, \ExtractIssue outputs a valid
  witness $(\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
  \rbrace_{j\in[n_j]})$ from each $\trans[\cid_i]$. This, concretely, implies
  that the $\yissue^i$ value available in $\trans[\cid_i]$ matches the one
  output by \fissue. Similarly, due to simulation extractability, the set of
  credentials $\lbrace \cid_{i,j}\rbrace_{j\in[n_i]}$ used to request credential
  $\cid_i$ cannot include credentials owned by different users, as this
  condition is ensured by $\NIZKRel_{\Issue}$. Thus, $\uid = \OWNR[\lbrace
  \cid_{i,j} \rbrace_{j\in[n_i]}] \neq \bot$. Now, assume that $\uid \notin \HU
  \cup \CU$. This, in addition to the fact that {\usk}s are produced uniformly
  at random, means that $\cred_i$ is not bound to a \usk owned by a known
  user. But then, $\cred_i$ cannot have been produced via \OBTISS or \ISSUE,
  which only accept requests from known {\uid}s (either in \HU or \CU,
  respectively). Thus, $\cred_i$ is a valid \SBCM signature, that has not been
  produced via an honest query, which breaks the one-more forgery property of
  \SBCM.

  \paragraph{(c) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:

@@

  \paragraph{(d) The output of \finsp matches the output of \Open.} %
  After (a), and correctness of the public key encryption algorihtm, the \yinsp
  value output by \Open is the correct decryption of
  \cinsp. After (c), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 13 is negligible due to simulation extractability
  of $\NIZK^{\Sign}$.

  \paragraph{(e) All {\cred}s are bound to the \usk of a known \uid.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accept calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}

>>>>

Next, we define the \SimSetup, \ExtractIssue, \ExtractSign functions. \SimSetup
(formally defined in \figref{fig:helper-funcs}) essentially replaces the
\Setup algorithm of each NIZK with the corresponding \NIZKSimSetup algorithm,
and returns the generated parameters along with the
trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
of the corresponding \NIZK scheme, leveraging the trapdoor produced during
\SimSetup. Note that, in our games definitions, both algorithms are always run
over signatures that have already been verified (in the case of \ExtractSign)
or transcripts maintained by honest issuers (in the case of \ExtractIssue).
Thus, the zero-knowledge proofs they contain are valid. Concerning \SimSetup,
due to the zero-knowledge and simulation extractability properties
(respectively) of the underlying NIZKs, its result is indistinguishable from
that of \Setup, and the extracted values match those used as witnesses in the
proofs.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(1^\secpar)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
        \Esecpar). \\
        % \Cparm \gets \CSetup(\Csecpar), 
        \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
        % \Sparm \gets \SSetup(\Ssecpar), 
        \Eparm \gets \ESetup(\Esecpar) \\
        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
        \pcreturn ((% \Cparm,
        \SBCMparm,% \Sparm,
        \Eparm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
        (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
      }

@@

\subsection{Issuance Unforgeability}

\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
  We show that the probability that \fissue outputs a wrong $\yissue$ value is
  negligible, as well as the probability that the issued credential, and any
  supporting credential used in the request, do not all belong to a same known
  (honest or corrupt) user.

  Observe that we restrict to credentials issued by honest issuers. Thus, if a
  credential with identifier \cid was issued by an honest issuer, a matching
  $\trans[\cid]$ entry corresponding to its issuance must exist.
  %
  Then, $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains a NIZK proof
  $\NIZKproof_{\Issue}$ proving knowledge by the (potentially corrupt) user of a
  witness in $\NIZKRel_{\Issue}$. Since the issuer is honest, it verifies the
  NIZK as part of the issuance protocol, rejecting if the proof is not valid.
  Thus, by simulation extractability, \ExtractIssue produces a $(\upk,\usk,
  \lbrace (\cid_i,\attrs_i,\cred_i) \rbrace_{i\in[n]},(\cid,\attrs,\cred))$
  tuple. Also due to simulation extractability, the value output by \fissue,
  when evaluated upon the extracted values, must match the \yissue value
  associated to $\trans[\cid]$.

  Finally, the adversary wins if the \uid associated to the {\cid}s involved in
  the request (i.e., both the \cid output by the adversary, as well as those
  used to support its issuance) is not in \HU or \CU. This can happen if: (1)
  all {\cid}s have the same owner \uid, but this \uid is different to all known
  {\uid}s; or (2) $\OWNR[\scid] = \bot$ which, by definition of \OWNR happens if
  not all of the involved {\cid}s in \scid have the same owner. Since the NIZK
  used for $\NIZKRel_{\Issue}$ is simulation extractable -- where the issuer
  verifies that all credentials are bound to the same \usk -- and due to
  correctness of \SBCM, the probability that (2) happens is negligible, which
  means that all involved {\cid}s have the same owner. Also, regarding (1), this
  owner must be in either \HU or \CU as the \cid output by the adversary in step
  2 has been produced via \ISSUE or \OBTISS which, by definition, only accept
  known {\uid}s. Thus, the probability that \adv~wins the \ExpForgeIssue game is
  negligible.
  \qed
\end{proof}

\subsection{Signature Unforgeability}

\begin{proof}[\thmref{thm:sign-forge-uas}; Signature unforgeability of \CUASGen]
  We show that an adversary \adv~winning \ExpForgeSign can be used to break the
  one-more unforgeability property of \SBCM.

  If the verification at line 4 of \ExpForgeSign holds, then $(\msg,\feval,
  \yeval,\cinsp,\sipk,\opk) \in \NIZKLang^{\Sign}$. Then:
  %

@@

  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:

@@

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), and correctness of the public key encryption algorihtm, the \yinsp
  value output by \Open is the correct decryption of
  \cinsp. After (c), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 13 is negligible due to simulation extractability
  of $\NIZK^{\Sign}$.

  \paragraph{(d) All {\cred}s are bound to the \usk of a known \uid.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accept calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}
